### 2011-05-16 Documentation/Article.tex
Add files for Insight Journal paper

%
% Complete documentation on the extended LaTeX markup used for Insight
% documentation is available in ``Documenting Insight'', which is part
% of the standard documentation for Insight.  It may be found online
% at:
%
%     http://www.itk.org/

\documentclass{InsightArticle}

\usepackage[dvips]{graphicx}

% Personal settings for code snippets visualization
\input{settings/TexCodeSet}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  hyperref should be the last package to be loaded.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[dvips,
bookmarks,
bookmarksopen,
backref,
colorlinks,linkcolor={blue},citecolor={blue},urlcolor={blue},
]{hyperref}

%  This is a template for Papers to the Insight Journal. 
%  It is comparable to a technical report format.

% The title should be descriptive enough for people to be able to find
% the relevant document. 
\title{}

% 
% NOTE: This is the last number of the "handle" URL that 
% The Insight Journal assigns to your paper as part of the
% submission process. Please replace the number "1338" with
% the actual handle number that you get assigned.
%
\newcommand{\IJhandlerIDnumber}{3196}

% Increment the release number whenever significant changes are made.
% The author and/or editor can define 'significant' however they like.
\release{0.00}

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{}
\authoraddress{ Harvard Medical School, Megason lab}

\begin{document}

% Add hyperlink to the web location and license of the paper.
\IJhandlefooter{\IJhandlerIDnumber}

\ifpdf
\else
   %
   % Commands for including Graphics when using latex
   %
   \DeclareGraphicsExtensions{.eps,.jpg,.gif,.tiff,.bmp,.png}
   \DeclareGraphicsRule{.jpg}{eps}{.jpg.bb}{`convert #1 eps:-}
   \DeclareGraphicsRule{.gif}{eps}{.gif.bb}{`convert #1 eps:-}
   \DeclareGraphicsRule{.tiff}{eps}{.tiff.bb}{`convert #1 eps:-}
   \DeclareGraphicsRule{.bmp}{eps}{.bmp.bb}{`convert #1 eps:-}
   \DeclareGraphicsRule{.png}{eps}{.png.bb}{`convert #1 eps:-}
\fi

\maketitle

\ifhtml
\chapter*{Front Matter\label{front}}
\fi

\begin{abstract}
\noindent
\end{abstract}

\IJhandlenote{\IJhandlerIDnumber}

\tableofcontents

\section{Introduction}
\section{Sikuli}
\section{Integration with CTest}
\section{Example}
\section{Conclusion}

\clearpage

\bibliographystyle{plain}
\bibliography{InsightJournal,AntoBib}

\end{document}

### 2011-06-08 Documentation/Article.tex
starts editing paper
authors
updated article

@@
 % the relevant document.
-\title{}
+\title{CTest Integration of Sikuli Automated GUI Testing}
 
@@
 % snail-mail address if you like.
-\author{}
-\authoraddress{ Harvard Medical School, Megason lab}
+\author{Evan Schwab, Lydie Souhait, Nicolas Rannou, Kishore Mosaliganti\\
+Arnaud Gelas, Sean Megason}
+\authoraddress{Harvard Medical School, Megason lab}
 
@@
 \tableofcontents
+% ------------------------------------------------------------------------
+\section{Introduction}
 
-\section{Introduction}
+% ------------------------------------------------------------------------
 \section{Sikuli}
+
+% Feel free to change section titles
+\subsection{What is sikuli?}
+Sikuli is a programming language that uses screen shot images as variables
+and objects in order to automate graphical user interface functions. The
+Sikuli program is comprised of an IDE where the user can write scripts that 
+include screen shot thumbnails so they can visually track the functions of
+their code. The Sikuli Script is built on a Jython (Python for Java platform)
+library which uses Python syntax in addition to a number of special Sikuli
+functions for aquiring and handling screenshot images and performing mouse,
+keyboard actions, the most useful of which are conveniently found as buttons
+on the Sikuli IDE.
+
+One of Sikuli's primary uses is the automation of GUI testing for software
+developers.
+
+\subsection{Simple of example} % not related to gofigure...
+
+\begin{figure}[htp]
+ \centering
+
+ \caption{here is my caption}
+ \label{fig:SimpleExample}
+\end{figure}
+
+% ------------------------------------------------------------------------
 \section{Integration with CTest}
+% I'll write it this part
+
+% ------------------------------------------------------------------------
 \section{Example}
+
+% ------------------------------------------------------------------------
 \section{Conclusion}

### 2011-06-09 Documentation/Article.tex
Updated Article.tex.  Need to figure out how to add the screen shot of sikuli script.
Began lead in to integration of CTest paragraph with discussion about Sikuli's Unit Testing feature.

@@
 keyboard actions, the most useful of which are conveniently found as buttons
-on the Sikuli IDE.
+on the Sikuli IDE.  Sikuli then saves a script in a directory with a unique
+extension .sikuli.  The directory consists of a the Sikuli script file in a 
+html file and as well as a Python script file and includes a list of all the 
+screenshot images used in the script.
 
-One of Sikuli's primary uses is the automation of GUI testing for software
-developers.
-
-\subsection{Simple of example} % not related to gofigure...
+\subsection{Simple Sikuli example} % not related to gofigure...
 
@@
 % I'll write it this part
+One of Sikuli's primary uses is the automation of GUI testing for software
+developers.  For GUI testing, it is useful to compartmentalize different software functions and test each unit
+individually.  The newest versions of Sikuli come equipped with a Unit Testing feature 
+Unit Testing.  Unit Testing can be called using the IDE or by command
+line and enables the user to write multiple functions in a script which are
+run individually.  At the end of the run, the Sikuli output will tell the user
+how many tests ran successfully and which ones failed and where.  To connect this
+Unit Testing feature directly to our software, we integrated Sikuli with CTest.
+.....
+.....
 

### 2011-06-09 Documentation/Article.tex
It now compiles
Add references

@@
 
-% Personal settings for code snippets visualization
-\input{settings/TexCodeSet}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 ]{hyperref}
+
+\usepackage{url}
 
@@
 \subsection{What is sikuli?}
-Sikuli is a programming language that uses screen shot images as variables
-and objects in order to automate graphical user interface functions. The
-Sikuli program is comprised of an IDE where the user can write scripts that 
-include screen shot thumbnails so they can visually track the functions of
-their code. The Sikuli Script is built on a Jython (Python for Java platform)
+
+Sikuli~\cite{Sikuli:Documentation,Sikuli:Website,Yeh:2009:Sikuli} is a visual
+technology to automate and test graphical user interfaces (GUI) using images
+(screenshots). Sikuli includes \emph{Sikuli Script} and \emph{Sikuli IDE}.\\
+
+\emph{Sikuli Script} automates anything you see on the screen without internal
+API's support. Sikuli Script is a programming language that uses screen shot
+images as variables and objects in order to automate graphical user interface
+functions. The Sikuli Script is built on a Jython (Python for Java platform)
 library which uses Python syntax in addition to a number of special Sikuli
-functions for aquiring and handling screenshot images and performing mouse,
-keyboard actions, the most useful of which are conveniently found as buttons
-on the Sikuli IDE.  Sikuli then saves a script in a directory with a unique
-extension .sikuli.  The directory consists of a the Sikuli script file in a 
-html file and as well as a Python script file and includes a list of all the 
-screenshot images used in the script.
+functions for acquiring and handling screen shot images and performing mouse,
+keyboard actions.\\
+
+In the \emph{Sikuli IDE}, the user can write scripts that include screen shot
+thumbnails so they can visually track the functions of their code. The most
+useful functions from Sikuli scripts are conveniently found as
+buttons on the IDE. When using the IDE, Sikuli then saves a script in a
+directory with a unique extension .sikuli. The directory consists of a python
+script file (script file to be used by sikuli), an html file, and a list of all
+the screenshot images used in the script.
 
@@
  \centering
-
  \caption{here is my caption}
@@
 \bibliographystyle{plain}
-\bibliography{InsightJournal,AntoBib}
+\bibliography{InsightJournal,biblio}
 

### 2011-06-09 Documentation/Article.tex
temp
integration with CTest

@@
 \section{Integration with CTest}
+
 % I'll write it this part
 One of Sikuli's primary uses is the automation of GUI testing for software
-developers.  For GUI testing, it is useful to compartmentalize different software functions and test each unit
-individually.  The newest versions of Sikuli come equipped with a Unit Testing feature 
-Unit Testing.  Unit Testing can be called using the IDE or by command
+developers. For GUI testing, it is useful to compartmentalize different software
+functions and test each unit individually.\\
+
+The newest versions of Sikuli come equipped with a Unit Testing feature based
+on JUnit~\cite{}. Unit Testing can be called using the IDE or by command
 line and enables the user to write multiple functions in a script which are
 run individually. At the end of the run, the Sikuli output will tell the user
-how many tests ran successfully and which ones failed and where.  To connect this
-Unit Testing feature directly to our software, we integrated Sikuli with CTest.
-.....
-.....
+how many tests ran successfully and which ones failed and where.\\
+
+Here we connect this Unit Testing feature to CTest, this allows us to report
+results on public dashboard using CDash.
 

### 2011-06-10 Documentation/Article.tex
Revert "Saved article.tex"
This reverts commit 01adb368dcb53845fd34cb6650e8845e402055e8.
Create Images directory
Updated graphic captions
Added explanation of simple example

@@
 
-\begin{figure}[htp]
+Figure 1 shows the Sikuli-IDE for version 0.10.2.  On the left-hand side menu is a list
+of commonly used Sikuli commands like find(), click(), and type().  The picture of
+the camera within the parentheses indicates the screenshot input variable.  Clicking
+on any of these menu functions will automatically set up the Sikuli screen shot mode, whereby
+the Sikuli-IDE disappears and what is on the screen at that moment is available to capture 
+by selecting a rectangular region of interest.  The function will then appear in the scripting domain
+with the snap shot in parentheses as shown in Figure 1.  The user may also type in the function
+and invoke the screen shot mode by clicking on the camera in the top menu or by using a
+keyboard shortcut. The simple Sikuli script example in Figure 1 will open gedit Text Editor, type a message,
+and save the file. (see Figure~\ref{fig:SimpleExample}).
+
+\begin{figure}[htbp]
  \centering
- \caption{here is my caption}
+ \includegraphics[width=0.99\textwidth]{Images/SimpleSikuliExample.png}
+ % SimpleSikuliExample.png: 1280x1024 pixel, 72dpi, 45.16x36.12 cm, bb=0 0 1280 1024
+ \caption{Simple Sikuli Script Example in Sikuli-IDE}
  \label{fig:SimpleExample}
@@
 
+Can you add comments in your example, please?
+
+\begin{figure}[htp]
+ \centering
+ \includegraphics[width=0.99\textwidth]{Images/Gofigure2Example.png}
+ % Gofigure2Example.png: 667x826 pixel, 72dpi, 23.53x29.14 cm, bb=0 0 667 826
+ \caption{Sikuli Script for Gofigure2 GUI Testing}
+ \label{fig:Gofigure2Example}
+\end{figure}
 % ------------------------------------------------------------------------

### 2011-06-10 Documentation/Article.tex
Updated explanation of Gofigure2 example script

@@
 
-Can you add comments in your example, please?
+The Sikuli script in Figure 2 shows a unit test for the GoFigure2 software.  The unit being tested here
+is the Toolbar menu which consists of different modes used to analyze data set plots, like zoom and pan.
+In total there are four modes which are represented in the first line as the vector Toolbar and for each
+of these modes we want to test their expected mouse functions.  For instance, if we are in the zoom Toolbar mode
+then we would want the data set plot to zoom in when the user scrolls the mouse wheel towards the computer.  Likewise,
+if we are in pan mode then we want the plot to move to the left if the user holds down the left mouse button and moves
+the mouse to the left.  Also importantly, we want to see that these two mouse actions are unique for their respective Toolbar modes.
+The test will include an assertion that scrolling forward will zoom in when using zoom mode and will do nothing when using pan mode.\\
+
+This breakdown of modes and actions lends itself to a nested for-loop scripting approach. In addition to representing the modes and actions
+as the vectors Toolbar and Mouse, respectively, we've included the different data set plots in the vector ViewRegion.
+These images represent the xy, xz, yz, xyz views of zebrafish microscopy data taken in the Megason Lab.  After capturing
+these images we can then use them to locate their initial xy pixel coordinates within the GoFigure2 GUI using the find() function.  These points become 
+our reference positions to calculate directional movement.  For example, when testing the pan mode, we mark the initial position of each image,
+use the mouseMove() function to a chosen location, and then use find() to obtain the new coordinates.  We can then assert if the image panned as it should have.
+Similarly for zoom, we can first find the area of the image and then find the area of the zoomed in image.  To test the result when the user clicks 
+in a certain mode, we've made use of Sikuli's assert exists() function to ascertain the existence of our
+desired results.        (see Figure~\ref{fig:Gofigure2Example}).
 

### 2011-06-10 Documentation/Article.tex
edited Example paragraph and included \emph{} for function names

--- 2011-06-10 Documentation/Article.tex
@@
 
-Can you add comments in your example, please?
+The Sikuli script in Figure 2 shows a fragment of a unit test for the GoFigure2 software.  The unit being tested here
+is the Toolbar menu which consists of different modes used to analyze data set plots.
+In total there are four modes which are represented in the first line as the vector Toolbar and for each
+of these modes we want to test their expected mouse functions.  For instance, if we are in the zoom Toolbar mode
+then we want the data set plot to zoom in when the user scrolls the mouse wheel forward.  Likewise,
+if we are in pan mode then we want the plot to move to the left if the user holds down the left mouse button and moves
+the mouse to the left.  Also importantly, we want to see that these two mouse actions are unique for their respective Toolbar modes;
+the test will include an assertion that scrolling forward will zoom in when using zoom mode and will do nothing when using pan mode.\\
+
+This breakdown of modes and actions lends itself to a nested for-loop scripting approach. In addition to representing the modes and actions
+as the vectors Toolbar and Mouse, respectively, we've included the different data set plots in the vector ViewRegion.
+These images represent the xy, xz, yz, and xyz views of zebrafish microscopy data taken in the Megason Lab.  After capturing
+these images we can then use them to locate their initial pixel coordinates within the GoFigure2 GUI using the \emph{find}() function.  These points become 
+our reference positions to calculate directional movement.  For example, when testing the pan mode, we mark the initial position of each image,
+use the \emph{mouseMove}() function to a chosen location, and then use \emph{find}() to obtain the new coordinates.  We can then assert if the image panned as it should have.
+Similarly for zoom, we can first find the area of the image and then find the area of the zoomed in image.  To test the result when the user clicks 
+in a certain mode, we've made use of Sikuli's \emph{assert exists}() function to ascertain the existence of our
+desired results   (see Figure~\ref{fig:Gofigure2Example}).
 

### 2011-06-10 Documentation/Article.tex
More edits and \emph{} to Example section

@@
 Figure 1 shows the Sikuli-IDE for version 0.10.2.  On the left-hand side menu is a list
-of commonly used Sikuli commands like find(), click(), and type().  The picture of
+of commonly used Sikuli commands like  \emph{find}(),  \emph{click}(), and  \emph{type}().  The picture of
 the camera within the parentheses indicates the screenshot input variable.  Clicking
@@
 
-This breakdown of modes and actions lends itself to a nested for-loop scripting approach. In addition to representing the modes and actions
+This breakdown of modes and actions lends itself to a nested for-loop scripting approach. By representing
+these variables as a vector the software developers can easily add new modes or actions to each list to be tested, when
+the software is updated. Similarly, the tester can easily replace any of the screenshot images with images of updated
+GUI icons.\\
+
+In addition to representing the modes and actions
 as the vectors Toolbar and Mouse, respectively, we've included the different data set plots in the vector ViewRegion.  
-These images represent the xy, xz, yz, and xyz views of zebrafish microscopy data taken in the Megason Lab.  After capturing
+These images represent the  \emph{xy-},  \emph{xz-},  \emph{yz-}, and  \emph{xyz-}views of zebrafish microscopy data taken in the Megason Lab.  After capturing
 these images we can then use them to locate their initial pixel coordinates within the GoFigure2 GUI using the \emph{find}() function.  These points become 
@@
 in a certain mode, we've made use of Sikuli's \emph{assert exists}() function to ascertain the existence of our
-desired results   (see Figure~\ref{fig:Gofigure2Example}).
+desired results   (see Figure~\ref{fig:Gofigure2Example}).\\
+
+This one GUI test is then combined with other GoFigure2 tests in succession and the Sikuli Unit Testing CTest integration will identify
+which tests pass and which fail and when. Many of the units need to be tested in a certain order.  For example, in order to test the Toolbar modes
+on the data sets, one first needs to test the software's data import functionality.
 

### 2011-06-16 Documentation/Article.tex
edit

@@
 
-Figure 1 shows the Sikuli-IDE for version 0.10.2.  On the left-hand side menu is a list
-of commonly used Sikuli commands like  \emph{find}(),  \emph{click}(), and  \emph{type}().  The picture of
-the camera within the parentheses indicates the screenshot input variable.  Clicking
-on any of these menu functions will automatically set up the Sikuli screen shot mode, whereby
-the Sikuli-IDE disappears and what is on the screen at that moment is available to capture 
-by selecting a rectangular region of interest.  The function will then appear in the scripting domain
-with the snap shot in parentheses as shown in Figure 1.  The user may also type in the function
-and invoke the screen shot mode by clicking on the camera in the top menu or by using a
-keyboard shortcut. The simple Sikuli script example in Figure 1 will open gedit Text Editor, type a message,
-and save the file. (see Figure~\ref{fig:SimpleExample}).
+Figure~\ref{fig:SimpleExample} shows the Sikuli-IDE for version 0.10.2. On the
+left-hand side menu is a list of commonly used Sikuli commands
+like \emph{find}(), \emph{click}(), and \emph{type}(). The picture of
+the camera within the parentheses indicates the screenshot input variable.
+Clicking on any of these menu functions will automatically set up the Sikuli
+screen shot mode, whereby the Sikuli-IDE disappears and what is on the screen at
+that moment is available to capture by selecting a rectangular region of
+interest. The function will then appear in the scripting domain with the snap
+shot in parentheses as shown in Figure~\ref{fig:SimpleExample}. The user may
+also type in the function and invoke the screen shot mode by clicking on the
+camera in the top menu or by using a keyboard shortcut. The simple Sikuli script
+example in Figure~\ref{fig:SimpleExample} will open gedit Text Editor, type a
+message, and save the file.
 
@@
  \label{fig:SimpleExample}
+\end{figure}
+
+% ------------------------------------------------------------------------
+\section{Example}
+
+The Sikuli script in Figure~\ref{fig:Gofigure2Example} shows a fragment of a
+unit test for the GoFigure2 software~\cite{GoFigure2:Website}. The unit being
+tested here is the Toolbar menu which consists of different modes used to
+analyze data set plots. In total there are four modes which are represented in
+the first line as the vector Toolbar and for each of these modes we want to test
+their expected mouse functions. For instance, if we are in the zoom Toolbar
+mode then we want the data set plot to zoom in when the user scrolls the mouse
+wheel forward. Likewise, if we are in pan mode then we want the plot to move to
+the left if the user holds down the left mouse button and moves the mouse to the
+left.  Also importantly, we want to see that these two mouse actions are unique
+for their respective Toolbar modes; the test will include an assertion that
+scrolling forward will zoom in when using zoom mode and will do nothing when
+using pan mode.\\
+
+This breakdown of modes and actions lends itself to a nested for-loop scripting
+approach. By representing these variables as a vector the software developers
+can easily add new modes or actions to each list to be tested, when the software
+is updated. Similarly, the tester can easily replace any of the screenshot
+images with images of updated GUI icons.\\
+
+In addition to representing the modes and actions as the vectors Toolbar and
+Mouse, respectively, we have included the different data set plots in the
+vector ViewRegion. These images represent the \emph{xy-}, \emph{xz-},
+\emph{yz-}, and \emph{xyz-}views of zebrafish microscopy data taken in the
+Megason Lab. After capturing these images we can then use them to locate their
+initial pixel coordinates within the GoFigure2 GUI using the \emph{find}()
+function. These points become our reference positions to calculate directional
+movement.  For example, when testing the pan mode, we mark the initial position
+of each image, use the \emph{mouseMove}() function to a chosen location, and
+then use \emph{find}() to obtain the new coordinates. We can then assert if the
+image panned as it should have. Similarly for zoom, we can first find the area
+of the image and then find the area of the zoomed in image.  To test the result
+when the user clicks in a certain mode, we've made use of Sikuli's \emph{assert
+exists}() function to ascertain the existence of our desired results (see
+Figure~\ref{fig:Gofigure2Example}).\\
+
+This one GUI test is then combined with other GoFigure2 tests in succession and
+the Sikuli Unit Testing CTest integration will identify which tests pass and
+which fail and when. Many of the units need to be tested in a certain order.
+For example, in order to test the Toolbar modes on the data sets, one first
+needs to test the software's data import functionality.
+
+\begin{figure}[htp]
+ \centering
+ \includegraphics[width=0.99\textwidth]{Images/Gofigure2Example.png}
+ % Gofigure2Example.png: 667x826 pixel, 72dpi, 23.53x29.14 cm, bb=0 0 667 826
+ \caption{Sikuli Script for Gofigure2 GUI Testing}
+ \label{fig:Gofigure2Example}
 \end{figure}
@@
 The newest versions of Sikuli come equipped with a Unit Testing feature based
-on JUnit~\cite{}. Unit Testing can be called using the IDE or by command
-line and enables the user to write multiple functions in a script which are
-run individually. At the end of the run, the Sikuli output will tell the user
-how many tests ran successfully and which ones failed and where.\\
+on JUnit~\cite{JUnit:Website}. Unit Testing can be called using the IDE or by
+command line and enables the user to write multiple functions in a script which
+are run individually. At the end of the run, the Sikuli output will tell the
+user how many tests ran successfully and which ones failed and where.\\
 
 Here we connect this Unit Testing feature to CTest, this allows us to report
-results on public dashboard using CDash.
+results on public dashboard using CDash. To this end, we developed cmake
+functions to discover where Sikuli is installed and special function to add
+sikuli test in the list of test for CTest.
 
-% ------------------------------------------------------------------------
-\section{Example}
+Here is a typical CMakeLists.txt file, to be able to use such functionalities:
 
-The Sikuli script in Figure 2 shows a fragment of a unit test for the GoFigure2 software.  The unit being tested here
-is the Toolbar menu which consists of different modes used to analyze data set plots.
-In total there are four modes which are represented in the first line as the vector Toolbar and for each
-of these modes we want to test their expected mouse functions.  For instance, if we are in the zoom Toolbar mode
-then we want the data set plot to zoom in when the user scrolls the mouse wheel forward.  Likewise,
-if we are in pan mode then we want the plot to move to the left if the user holds down the left mouse button and moves
-the mouse to the left.  Also importantly, we want to see that these two mouse actions are unique for their respective Toolbar modes;
-the test will include an assertion that scrolling forward will zoom in when using zoom mode and will do nothing when using pan mode.\\
+\begin{verbatim}
+# first let's include CTest and enable testing
 
-This breakdown of modes and actions lends itself to a nested for-loop scripting approach. By representing
-these variables as a vector the software developers can easily add new modes or actions to each list to be tested, when
-the software is updated. Similarly, the tester can easily replace any of the screenshot images with images of updated
-GUI icons.\\
+include( CTest )
+enable_testing()
 
-In addition to representing the modes and actions
-as the vectors Toolbar and Mouse, respectively, we've included the different data set plots in the vector ViewRegion.  
-These images represent the  \emph{xy-},  \emph{xz-},  \emph{yz-}, and  \emph{xyz-}views of zebrafish microscopy data taken in the Megason Lab.  After capturing
-these images we can then use them to locate their initial pixel coordinates within the GoFigure2 GUI using the \emph{find}() function.  These points become 
-our reference positions to calculate directional movement.  For example, when testing the pan mode, we mark the initial position of each image,
-use the \emph{mouseMove}() function to a chosen location, and then use \emph{find}() to obtain the new coordinates.  We can then assert if the image panned as it should have.
-Similarly for zoom, we can first find the area of the image and then find the area of the zoomed in image.  To test the result when the user clicks 
-in a certain mode, we've made use of Sikuli's \emph{assert exists}() function to ascertain the existence of our
-desired results   (see Figure~\ref{fig:Gofigure2Example}).\\
+# Then let's
+#   - figure out where Sikuli is installed
+#   - define function to add Sikuli tests
 
-This one GUI test is then combined with other GoFigure2 tests in succession and the Sikuli Unit Testing CTest integration will identify
-which tests pass and which fail and when. Many of the units need to be tested in a certain order.  For example, in order to test the Toolbar modes
-on the data sets, one first needs to test the software's data import functionality.
+find_package( Sikuli )
 
-\begin{figure}[htp]
- \centering
- \includegraphics[width=0.99\textwidth]{Images/Gofigure2Example.png}
- % Gofigure2Example.png: 667x826 pixel, 72dpi, 23.53x29.14 cm, bb=0 0 667 826
- \caption{Sikuli Script for Gofigure2 GUI Testing}
- \label{fig:Gofigure2Example}
-\end{figure}
+# here we add a sikuli test
+add_sikuli_test( ThunderbirdSikuliTest test.sikuli )
+\end{verbatim}
+
+Users can either maintain an image library, either keep images in the
+corresponding sikuli script directory (default). If one use an image library,
+the corresponding path must be set during CMake time in
+the SIKULI\_IMAGE\_LIBRARY\_DIR variable.
+
 % ------------------------------------------------------------------------

### 2011-06-17 Documentation/Article.tex
Working on Intro

@@
 \noindent
+
 \end{abstract}
@@
 \section{Introduction}
-
+GUI testing is a key aspect of software development. Having a well defined testing protocol is very
+important in maintaining a productive flow, especially on the eve of a new release.  The number of units
+to test is greatly compounded as the software becomes more complex and keeping up with the complexity can be
+immensely time consuming.  We collected a list of over 400 different but very repetitive GUI tests which
+involved endless clicking and checking.  This task took around 5 hours to complete each time a new release was ready.
+Then debugging would push release dates back days or even weeks.   
 % ------------------------------------------------------------------------

### 2011-06-17 Documentation/Article.tex
Completed draft of Intro.  Also included questions in comments.

--- 2011-06-16 Documentation/Article.tex
@@
 \section{Introduction}
+
+%Should this be in the abstract instead?
+% difference between Abstract and Introduction?
+
+GUI testing is a key aspect of software development. Having a well defined testing protocol is very
+important in maintaining a productive flow, especially on the eve of a new release.  As the software becomes 
+more complex, testing each feature can be immensely time consuming.  
+We collected a list of over 400 different GUI tests which
+involved endlessly repetitive clicking and checking.  This task took around 5 hours to complete each time a new release was ready.
+And debugging would push release dates back days or even weeks.  We decided to tackle this problem by utilizing a new
+scripting language called Sikuli that can automate any visual operation.  In this way we could write scripts to automate the GUI testing.
+This cut the time to complete each test drastically.  Furthermore, we have integrated the automated tests with CTest.  Therefore we will be able to
+run the collection of tests every night and find bugs as they arise instead of the night before a new release.  As a result,
+the rate of new releases increased drastically.
+
+% Should the intro be about GoFigure2? with picture of GoFigure2
+% Also consult actual number of tests.
+%See Figure 3 ? -- picture of GIT log from presentation
 

### 2011-06-17 Documentation/Article.tex
Added GoFigure2 GUI screenshot.  Included description of GoFigure2 software in GoFigure2 example section.

@@
 
-The Sikuli script in Figure~\ref{fig:Gofigure2Example} shows a fragment of a
-unit test for the GoFigure2 software~\cite{GoFigure2:Website}. The unit being
+The GoFigure2 software~\cite{GoFigure2:Website} (See Figure~\ref{fig:GoFigure2GUI}) is designed to automate 
+cell segmentation and tracking for high resolution microscopy data and the Megason Lab uses it to
+create cell lineages of developing zebrafish emrbryos. The Sikuli script in Figure~\ref{fig:Gofigure2Example} shows a fragment of a
+unit test for our GoFigure2 software.   The unit being
 tested here is the Toolbar menu which consists of different modes used to
@@
 needs to test the software's data import functionality.
+
+\begin{figure}[htbp]
+ \centering
+ \includegraphics[width=0.99\textwidth]{Images/Gofigure2GUI.png}
+ % SimpleSikuliExample.png: 1280x1024 pixel, 72dpi, 45.16x36.12 cm, bb=0 0 1280 1024
+ \caption{GoFigure2 GUI Interface}
+ \label{fig:GoFigure2GUI}
+\end{figure}
 

### 2011-06-17 Documentation/Article.tex
limitations

@@
 % snail-mail address if you like.
-\author{Evan Schwab, Lydie Souhait, Nicolas Rannou, Kishore Mosaliganti\\
-Arnaud Gelas, Sean Megason}
-\authoraddress{Harvard Medical School, Megason lab}
+\author{Evan Schwab, Arnaud Gelas, Lydie Souhait, Nicolas Rannou,\\
+Kishore Mosaliganti, Sean Megason}
+\authoraddress{Megason Lab, Department of Systems Biology, Harvard Medical
+School}
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}[tbp]
  \centering
@@
 
-The GoFigure2 software~\cite{GoFigure2:Website} (See Figure~\ref{fig:GoFigure2GUI}) is designed to automate 
-cell segmentation and tracking for high resolution microscopy data and the Megason Lab uses it to
-create cell lineages of developing zebrafish emrbryos. The Sikuli script in Figure~\ref{fig:Gofigure2Example} shows a fragment of a
-unit test for our GoFigure2 software.   The unit being
-tested here is the Toolbar menu which consists of different modes used to
-analyze data set plots. In total there are four modes which are represented in
-the first line as the vector Toolbar and for each of these modes we want to test
-their expected mouse functions. For instance, if we are in the zoom Toolbar
-mode then we want the data set plot to zoom in when the user scrolls the mouse
-wheel forward. Likewise, if we are in pan mode then we want the plot to move to
-the left if the user holds down the left mouse button and moves the mouse to the
-left.  Also importantly, we want to see that these two mouse actions are unique
-for their respective Toolbar modes; the test will include an assertion that
-scrolling forward will zoom in when using zoom mode and will do nothing when
-using pan mode.\\
+The GoFigure2 software~\cite{GoFigure2:Website} (See
+Figure~\ref{fig:GoFigure2GUI}) is designed to automate
+cell segmentation and tracking for high resolution microscopy data and the
+Megason Lab uses it to create cell lineages of developing zebrafish emrbryos.
+The Sikuli script in Figure~\ref{fig:Gofigure2Example} shows a fragment of a
+unit test for our GoFigure2 software. The unit being tested here is the Toolbar
+menu which consists of different modes used to analyze data set plots. In total
+there are four modes which are represented in the first line as the vector
+Toolbar and for each of these modes we want to test their expected
+mouse functions. For instance, if we are in the zoom Toolbar mode then we want
+the data set plot to zoom in when the user scrolls the mouse wheel
+forward. Likewise, if we are in pan mode then we want the plot to move to the
+left if the user holds down the left mouse button and moves the mouse to
+the left. Also importantly, we want to see that these two mouse actions are
+unique for their respective Toolbar modes; the test will include an assertion
+that scrolling forward will zoom in when using zoom mode and will do nothing
+when using pan mode.\\
+
+\begin{figure}[tbp]
+ \centering
+ \includegraphics[width=0.99\textwidth]{Images/Gofigure2GUI.png}
+ % SimpleSikuliExample.png: 1280x1024 pixel, 72dpi, 45.16x36.12 cm, bb=0 0 1280
+ \caption{GoFigure2 GUI Interface}
+ \label{fig:GoFigure2GUI}
+\end{figure}
 
@@
 
-\begin{figure}[htbp]
- \centering
- \includegraphics[width=0.99\textwidth]{Images/Gofigure2GUI.png}
- % SimpleSikuliExample.png: 1280x1024 pixel, 72dpi, 45.16x36.12 cm, bb=0 0 1280 1024
- \caption{GoFigure2 GUI Interface}
- \label{fig:GoFigure2GUI}
-\end{figure}
-
-\begin{figure}[htp]
+\begin{figure}[tbp]
  \centering
@@
 % ------------------------------------------------------------------------
+\section{Current Limitation}
+
+\subsection{Text Recognition}
+
+\subsection{Off-screen Rendering}
+
+\subsection{Variation of style between machines}
+Different OS, different look => failures
+Even on the same OS, GUI can look different = > failures
+
+\subsection{CDash}
+
+% ------------------------------------------------------------------------
 \section{Conclusion}

### 2011-06-17 Documentation/Article.tex
some more edits

@@
 
-GUI testing is a key aspect of software development. Having a well defined testing protocol is very
-important in maintaining a productive flow, especially on the eve of a new release.  As the software becomes 
-more complex, testing each feature can be immensely time consuming.  
-We collected a list of over 400 different GUI tests which
-involved endlessly repetitive clicking and checking.  This task took around 5 hours to complete each time a new release was ready.
-And debugging would push release dates back days or even weeks.  We decided to tackle this problem by utilizing a new
-scripting language called Sikuli that can automate any visual operation.  In this way we could write scripts to automate the GUI testing.
-This cut the time to complete each test drastically.  Furthermore, we have integrated the automated tests with CTest.  Therefore we will be able to
-run the collection of tests every night and find bugs as they arise instead of the night before a new release.  As a result,
-the rate of new releases increased drastically.
+GUI testing is a key aspect of software development. Having a well defined
+testing protocol is very important in maintaining a productive flow, especially
+on the eve of a new release. As the software becomes more complex, testing each
+feature can be immensely time consuming. We collected a list of over 400
+different GUI tests for the GoFigure2 software~\cite{GoFigure2:Website} which
+involved endlessly repetitive clicking and checking. This task took around 5
+hours to complete each time a new release was ready. And debugging would push
+release dates back days or even weeks. We decided to tackle this problem by
+utilizing a new scripting language called
+Sikuli~\cite{Sikuli:Documentation,Sikuli:Website,Yeh:2009:Sikuli} that can
+automate any visual operation. In this way we could write scripts to automate
+the GUI testing. This cut the time to complete each test drastically.
+Furthermore, we have integrated the automated tests with CTest. Therefore we
+are able to run the collection of tests every night and find bugs as they
+arise instead of the night before a new release. As a result, the rate of new
+releases increased drastically.\\
+
+The paper is organized as follows, first we will briefly introduce what is
+Sikuli (in section~\ref{sec:WhatIsSikuli}) and show one simple example (in
+section~\ref{sec:SimpleSikuliExample}). Then we will show a real test example
+on GoFigure2 (in section~\ref{sec:GoFigure2Example}) and how to integrate
+unit tests in CTest (in section~\ref{sec:IntegrationWithCTest}). Finally, we
+will review the current limitation of Sikuli and this approach for GUI Testing
+(in section~\ref{sec:Limitations}) and conclude (in
+section~\ref{sec:Conclusion}).
 
@@
 % Feel free to change section titles
-\subsection{What is sikuli?}
+\subsection{What is Sikuli?}
+\label{sec:WhatIsSikuli}
 
@@
 
+% ------------------------------------------------------------------------
 \subsection{Simple Sikuli example} % not related to gofigure...
+\label{sec:SimpleSikuliExample}
 
@@
 \section{Example}
+\label{sec:GoFigure2Example}
 
@@
 \section{Integration with CTest}
+\label{sec:IntegrationWithCTest}
 
@@
 # here we add a sikuli test
-add_sikuli_test( ThunderbirdSikuliTest test.sikuli )
+add_sikuli_test( GoFigure2ToolbarTest toolbar.sikuli )
 \end{verbatim}
@@
 % ------------------------------------------------------------------------
-\section{Current Limitation}
+\section{Current Limitations}
+\label{sec:Limitations}
 
@@
 \section{Conclusion}
+\label{sec:Conclusion}
 

### 2011-06-17 Documentation/Article.tex
Included limitation subsections off screen rendering and variation between machines.  Deleted Text recognition for now.

@@
 
-\subsection{Text Recognition}
-
+Sikuli's integration with CTest has provided us with numerous advantages in the
+measure of productivity and convenience. But our goals are still
+hindered by a few limitations.
+%\subsection{Text Recognition}
+%Sikuli's newer versions come equipped with a text recognition feature whereby
+%one can search for a string of text instead of searching for the image of the
+%text in the GUI.  This makes programming in Sikuli much simpler but it is
+%limited by it's searchable text fonts.
 \subsection{Off-screen Rendering}
-
+Our goal in using CTest is that we will be able to test our software
+automatically every night and bugs can be reported the next day on CDash.  But
+Sikuli is not easily compatible with off-screen rendering.  Sikuli requires
+that the screen remains on so that the script can identify the images on the
+screen.  In addition, external mouse and keyboard actions can disrupt the script
+at any moment.  These factors make it more difficult to set up automated
+nightly tests.  
 \subsection{Variation of style between machines}
-Different OS, different look => failures
-Even on the same OS, GUI can look different = > failures
-
+%Different OS, different look => failures
+%Even on the same OS, GUI can look different = > failures
+Another important issue is the difference between operating systems. 
+Developers need to make sure that their software runs on each
+OS.  But Different operating systems require different libraries for
+generating GUI images. Therefore fonts, icons, and even
+layouts will differ between machines. This is also true between versions of the
+same OS. So, GUI tests that pass on one machine will inevitably fail on another
+machine for the same exact software. This requires developers to write the
+same Sikuli script using images from each OS, which will be many times the
+workload.  
 \subsection{CDash}

### 2011-06-20 Documentation/Article.tex
changed all "screen shot" to "screenshot"

@@
 \emph{Sikuli Script} automates anything you see on the screen without internal
-API's support. Sikuli Script is a programming language that uses screen shot
+API's support. Sikuli Script is a programming language that uses screenshot
 images as variables and objects in order to automate graphical user interface
@@
 library which uses Python syntax in addition to a number of special Sikuli
-functions for acquiring and handling screen shot images and performing mouse,
+functions for acquiring and handling screenshot images and performing mouse,
 keyboard actions.\\
 
-In the \emph{Sikuli IDE}, the user can write scripts that include screen shot
+In the \emph{Sikuli IDE}, the user can write scripts that include screenshot
 thumbnails so they can visually track the functions of their code. The most
@@
 Clicking on any of these menu functions will automatically set up the Sikuli
-screen shot mode, whereby the Sikuli-IDE disappears and what is on the screen at
+screenshot mode, whereby the Sikuli-IDE disappears and what is on the screen at
 that moment is available to capture by selecting a rectangular region of
@@
 shot in parentheses as shown in Figure~\ref{fig:SimpleExample}. The user may
-also type in the function and invoke the screen shot mode by clicking on the
+also type in the function and invoke the screenshot mode by clicking on the
 camera in the top menu or by using a keyboard shortcut. The simple Sikuli script

### 2011-06-21 test2.sikuli/test2.py
Remove test4

@@ -2,8 +2,8 @@ def setUp(self):
   print "setUp";
 
 def testA(self):
-  print "failing test";
-  assertExist( "1301610526405.png" );
+  print "syntax error";
+  unclick();
 
 def tearDown(self):
   print "tearDown";

### 2011-06-21 test3.sikuli/test3.py

@@ -1,6 +1,5 @@
 from sikuli.Sikuli import *
 
 def mytest(self):
-	print "mytest";
-	
-	
+	print "test3";
+

### 2011-06-21 test2.sikuli/test2.py
wrap it up

@@ -1,7 +1,7 @@
 def setUp(self):
   print "setUp";
 
-def testA(self):
+def testSyntaxError(self):
   print "syntax error";
   unclick();
 

### 2011-06-21 test3.sikuli/test3.py

@@ -1,5 +1,9 @@
-from sikuli.Sikuli import *
+def setUp(self):
+  print "setUp";
 
-def mytest(self):
-	print "test3";
+def testPrint(self):
+  print "dummy test to validate, it is printing on the screen!";
+
+def tearDown(self):
+  print "tearDown";
 

### 2011-06-21 Documentation/Article.tex
Filled in Unit Testing subsection with verbatim def script.

@@
 
-% I'll write it this part
+\subsection{CMake}
+
 One of Sikuli's primary uses is the automation of GUI testing for software
@@
 
-Here we connect this Unit Testing feature to CTest, this allows us to report
-results on public dashboard using CDash. To this end, we developed cmake
-functions to discover where Sikuli is installed and special function to add
-sikuli test in the list of test for CTest.
+Here we connect this Unit Testing feature to CTest, which allows us to report
+results on a public dashboard using CDash. To this end, we developed cmake
+functions to discover where Sikuli is installed and special functions to add
+Sikuli tests in the list for CTest.
 
@@
 
-Users can either maintain an image library, either keep images in the
-corresponding sikuli script directory (default). If one use an image library,
+Users can either maintain an image library or keep images in the
+corresponding Sikuli script directory (default). If one uses an image library,
 the corresponding path must be set during CMake time in
 the SIKULI\_IMAGE\_LIBRARY\_DIR variable.
+
+\subsection{Unit Test Script Format}
+
+Unit testing scripts are written as a series of functions defined by pythons
+keyword def.  The constructing and destructing methods,
+\emph{setUp}() and \emph{tearDown}(), are used to start and end the software
+GUI and methods in between are named with the prefix test.
+
+\begin{verbatim}
+def setUp(self):
+  print "setUp";
+
+def testPrint(self):
+  print "dummy test to validate, it is printing on the screen!";
+
+def tearDown(self):
+  print "tearDown";
+\end{verbatim}
+
+When this script is run with the Sikuli Unit Testing feature, it will report the
+results of each test method in CTest and then reported automatically on
+CDash.
 
@@
 workload.
+
 \subsection{CDash}
+Furthermore, CDash does not currently support Sikuli script since images used
+in the script are unable to be displayed on the dashboard.  Without these
+images on CDash, visualize which units are being tested.  In addition, CDash
+does not make the distinction between simple syntax errors versus a complete
+test failure. These are
+extensions to CDash that can be corrected for future work.
 

### 2011-06-21 Documentation/Article.tex
minor edits

--- 2011-06-20 Documentation/Article.tex
@@
 hindered by a few limitations.
+
 %\subsection{Text Recognition}
@@
 %limited by it's searchable text fonts.
+
 \subsection{Off-screen Rendering}
+
 Our goal in using CTest is that we will be able to test our software 
-automatically every night and bugs can be reported the next day on CDash.  But
-Sikuli is not easily compatible with off-screen rendering.  Sikuli requires
-that the screen remains on so that the script can identify the images on the
-screen.  In addition, external mouse and keyboard actions can disrupt the script
-at any moment.  These factors make it more difficult to set up automated
-nightly tests.  
+automatically every night and bugs can be reported the next day on CDash. 
+But Sikuli is not easily compatible with off-screen rendering. Sikuli 
+requires that the screen remains on so that the script can identify the 
+images on the screen. In addition, external mouse and keyboard actions can 
+disrupt the script at any moment. These factors make it more difficult to 
+set up automated nightly tests.
+
 \subsection{Variation of style between machines}
-%Different OS, different look => failures
-%Even on the same OS, GUI can look different = > failures
+
 Another important issue is the difference between operating systems.
-Developers need to make sure that their software runs on each
-OS.  But Different operating systems require different libraries for
-generating GUI images. Therefore fonts, icons, and even
-layouts will differ between machines. This is also true between versions of the
-same OS. So, GUI tests that pass on one machine will inevitably fail on another
-machine for the same exact software. This requires developers to write the
-same Sikuli script using images from each OS, which will be many times the
-workload.  
+Developers need to make sure that their software runs on each OS. But
+Different operating systems require different libraries for generating GUI
+images. Therefore fonts, icons, and even layouts will differ between
+machines. This is also true between versions of the same OS. So, GUI tests
+that pass on one machine will inevitably fail on another machine for the
+same exact software. This requires developers to write the same Sikuli 
+script using images from each OS, which will be many times the workload.
+
 \subsection{CDash}

### 2011-06-21 Documentation/Article.tex

--- 2011-06-21 Documentation/Article.tex
@@
 %limited by it's searchable text fonts.
+
 \subsection{Off-screen Rendering}
+
 Our goal in using CTest is that we will be able to test our software 
-automatically every night and bugs can be reported the next day on CDash.  But
-Sikuli is not easily compatible with off-screen rendering.  Sikuli requires
-that the screen remains on so that the script can identify the images on the
-screen.  In addition, external mouse and keyboard actions can disrupt the script
-at any moment.  These factors make it more difficult to set up automated
-nightly tests.  
+automatically every night and bugs can be reported the next day on CDash. 
+But Sikuli is not easily compatible with off-screen rendering. Sikuli 
+requires that the screen remains on so that the script can identify the 
+images on the screen. In addition, external mouse and keyboard actions can 
+disrupt the script at any moment. These factors make it more difficult to 
+set up automated nightly tests.
+
 \subsection{Variation of style between machines}
-%Different OS, different look => failures
-%Even on the same OS, GUI can look different = > failures
+
 Another important issue is the difference between operating systems.
-Developers need to make sure that their software runs on each
-OS.  But Different operating systems require different libraries for
-generating GUI images. Therefore fonts, icons, and even
-layouts will differ between machines. This is also true between versions of the
-same OS. So, GUI tests that pass on one machine will inevitably fail on another
-machine for the same exact software. This requires developers to write the
-same Sikuli script using images from each OS, which will be many times the
-workload.
+Developers need to make sure that their software runs on each OS. But
+Different operating systems require different libraries for generating GUI
+images. Therefore fonts, icons, and even layouts will differ between
+machines. This is also true between versions of the same OS. So, GUI tests
+that pass on one machine will inevitably fail on another machine for the
+same exact software. This requires developers to write the same Sikuli 
+script using images from each OS, which will be many times the workload.
 

### 2011-06-21 Documentation/Article.tex
minor edit
to be submitted

--- 2011-06-21 Documentation/Article.tex
@@
 \noindent
-
+In order to test our software GoFigure2~\cite{GoFigure2:Website} (for the
+visualization and the processing of extremely large $3D+t$ microscopy images),
+we utilized the visual programming technology Sikuli~\cite{Sikuli:Website} to
+automate our GUI testing. We then integrated these Sikuli tests into CTest and
+used CDash to report the results on a dashboard with the view to test our
+software automatically every night and detect bugs as soon as they occur.  Our
+rate of releases more than doubled as a result.
 \end{abstract}
@@
 arise instead of the night before a new release. As a result, the rate of new
-releases increased drastically.\\
+releases increased drastically from one
+release every five months to one release every two months. \\
 
@@
 buttons on the IDE. When using the IDE, Sikuli then saves a script in a
-directory with a unique extension .sikuli. The directory consists of a python
-script file (script file to be used by sikuli), an html file, and a list of all
+directory with a unique extension .Sikuli. The directory consists of a python
+script file (script file to be used by Sikuli), an html file, and a list of all
 the screenshot images used in the script.
@@
  \includegraphics[width=0.99\textwidth]{Images/SimpleSikuliExample.png}
- % SimpleSikuliExample.png: 1280x1024 pixel, 72dpi, 45.16x36.12 cm, bb=0 0 1280 1024
+ % SimpleSikuliExample.png: 1280x1024 pixel, 72dpi, 45.16x36.12 cm, bb=0 0 1280
+1024
  \caption{Simple Sikuli Script Example in Sikuli-IDE}
@@
 
-# here we add a sikuli test
-add_sikuli_test( GoFigure2ToolbarTest toolbar.sikuli )
+# here we add a Sikuli test
+add_Sikuli_test( GoFigure2ToolbarTest toolbar.Sikuli )
 \end{verbatim}
@@
 does not make the distinction between simple syntax errors versus a complete
-test failure. These are
-extensions to CDash that can be corrected for future work.
+test failure. These are extensions to CDash that can be corrected for future
+work.
 
@@
 \label{sec:Conclusion}
+In this paper we discussed the uses of Sikuli unit testing and how they can be
+integrated into CTest.  Although we have recognized limitations within the
+current infrastructure (Sikuli and CDash), there is great potential to make
+these technologies more universal thanks to the fast growing Sikuli
+community. The results of our increased productivity have proven this
+technology well worth the effort.\\
+
+Due to the previous exposed limitations (see section~\ref{sec:Limitations}),
+provided examples may not run on your machine. However, it is easy enough to
+adapt these tests to your system.
+
+\section*{Note}
+As of now, Sikuli has been successfully integrated with CTest on
+linux, and it
+requires some more work for Windows and Mac. We would welcome
+contributions to make it happen!
 

### 2011-06-21 Documentation/Article.tex
submitted version

@@
 \noindent
-In order to test our software GoFigure2~\cite{GoFigure2:Website} (for the
-visualization and the processing of extremely large $3D+t$ microscopy images),
+In order to test our software GoFigure2~\cite{GoFigure2:Website} for the
+visualization and the processing of extremely large $3D+t$ microscopy images,
 we utilized the visual programming technology Sikuli~\cite{Sikuli:Website} to
@@
 software automatically every night and detect bugs as soon as they occur.  Our
-rate of releases more than doubled as a result.
+rate of releases more than doubled as a result.\\
+
+\noindent Source code and examples are available
+here:~\url{https://github.com/gofigure2/SikuliCTest}
 \end{abstract}

### 2011-06-23 test.sikuli/test.py
Change example test to launch firefox, go to midasjournal website
(and search for sikuli's paper)

@@ -1,9 +1,13 @@
 def setUp(self):
-  print "setUp";
+	print "setUp";
 
-def testThunderbird(self):
-  print "Click on thunderbird";
-  click("1299697212820.png")
+def testFirefox(self):
+	print "Click on firefox";
+	click("1308851838899.png")
+	doubleClick("1308852041788.png")
+	type("http://midasjournal.org"+Key.ENTER)
+	click("1308852315244.png")
+	type("sikuli"+Key.ENTER)
 
 def tearDown(self):
-  print "tearDown";
+	print "tearDown";

### 2011-06-23 test.sikuli/test.py
add some wait to make sure previous actions get done

@@ -4,10 +4,13 @@ def setUp(self):
 def testFirefox(self):
 	print "Click on firefox";
 	click("1308851838899.png")
+	wait(10)
 	doubleClick("1308852041788.png")
 	type("http://midasjournal.org"+Key.ENTER)
+	wait(10)
 	click("1308852315244.png")
 	type("sikuli"+Key.ENTER)
 
 def tearDown(self):
 	print "tearDown";
+
